---
title: "p8105_hw1_xw2417"
author: "Xun Wang"
date: "9/20/2019"
output: github_document
---

This is the solution for P8105 homework 1 from Xun Wang.

```{r setup, include = FALSE}
library(tidyverse)
```

## Problem 1

The code chunk below **creates a dataframe** compromised of a random sample of size 8 from a standard Normal distribution, a logical vector indicating whether elements of the sample are greater than 0, a character vector of length 8, a factor vector of length 8 with 3 different factor “levels”.

```{r df_create}
set.seed(1234)

hw_df = tibble(
  vec_numeric = rnorm(8),
  vec_logical = vec_numeric > 0,
  vec_char = c("This","is", "the", "first", "data", "frame", "from", "Xun")，
  vec_factor = factor(c("he", "he", "he", "she", "she", "she", "they", "they"))
)

## The code below tries to take the mean of each variable in my dateframe.

mean_numeric = mean(pull(hw_df, vec_numeric))
mean_logical = mean(pull(hw_df, vec_logical))
mean_char = mean(pull(hw_df, vec_char))
mean_factor = mean(pull(hw_df, vec_factor))
```

**Summary 1:** The **"mean"** works for numeric and logical variables but not for character or factor variables if the argument is not numeric or logical.

The code chunk below **converts** the logical vector to numeric or a factor and **multiplies** the random sample by the result. And it converts the logical vector to a factor and then converts the result to numeric, and multiplies the random sample by the result.

```{r df_convert}
as.numeric(pull(hw_df, vec_logical))*pull(hw_df, vec_numeric)
as.factor(pull(hw_df, vec_logical))*pull(hw_df, vec_numeric)
as.numeric(as.factor(pull(hw_df, vec_logical)))*pull(hw_df, vec_numeric)
```

**Summary 2:** logical variables can be multiplied with numeric variables, but factors can't be multiplies.

## Problem 2

The code chunk

