---
title: "p8105_hw1_xw2417"
author: "Xun Wang"
date: "9/20/2019"
output: github_document
---

This is the solution for P8105 homework 1 from Xun Wang.

```{r setup, include = FALSE}
library(tidyverse)
```

## Problem 1

The code chunk below **creates a dataframe** compromised of a random sample of size 8 from a standard Normal distribution, a logical vector indicating whether elements of the sample are greater than 0, a character vector of length 8, a factor vector of length 8 with 3 different factor “levels”.

```{r problem_1}
set.seed(1234)

prob1_df = tibble(
  vec_numeric = rnorm(8),
  vec_logical = vec_numeric > 0,
  vec_char = c("This","is", "the", "first", "data", "frame", "from", "Xun")，
  vec_factor = factor(c("he", "he", "he", "she", "she", "she", "they", "they"))
)

## The code below tries to take the mean of each variable in my dateframe.

mean_numeric = mean(pull(prob1_df, vec_numeric))
mean_logical = mean(pull(prob1_df, vec_logical))
mean_char = mean(pull(prob1_df, vec_char))
mean_factor = mean(pull(prob1_df, vec_factor))
```

**Summary 1:** The **"mean"** works for numeric and logical variables but not for character or factor variables if the argument is not numeric or logical.

The code chunk below **converts** the logical vector to numeric or a factor and **multiplies** the random sample by the result. And it converts the logical vector to a factor and then converts the result to numeric, and multiplies the random sample by the result.

```{r df_convert}
as.numeric(pull(prob1_df, vec_logical))*pull(prob1_df, vec_numeric)
as.factor(pull(prob1_df, vec_logical))*pull(prob1_df, vec_numeric)
as.numeric(as.factor(pull(prob1_df, vec_logical)))*pull(prob1_df, vec_numeric)
```

**Summary 2:** Logical variables can be multiplied with numeric variables, but factors can't be multiplies.

## Problem 2

The code chunk below creates a data frame comprised of x and y both from random sampling of size 500 from a standard Normal distribution.

```{r problem_2}
set.seed(1234)

prob2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_logical = x + y > 1,
  vec_numeric = as.numeric(vec_logical),
  vec_factor = as.factor(vec_logical)
)

df_nrow = nrow(prob2_df)
df_ncol = ncol(prob2_df)
x_mean = mean(pull(prob2_df, x))
x_median = median(pull(prob2_df, x))
x_sd = sd(pull(prob2_df, x))
pos_prop = sum(pull(prob2_df, vec_logical)) / length(pull(prob2_df, vec_logical))

```

The vector created above is `r df_nrow` rows * `r df_ncol` columns. The mean of x is `r x_mean`. The median of x is `r x_median`. The standard deviationof x is `r x_sd`. The proportion of cases for which x + y > 1 is `r pos_prop`.

This code chunk makes scatterplots of y vs x colored by logical variables created in Problem 2 data frame.

```{r yx_scatter_logical}
ggplot(prob2_df, aes(x = x, y = y, color = vec_logical)) + geom_point() + labs(color = "x + y > 1")
```

This code chunk makes scatterplots of y vs x colored by numeric variables created in Problem 2 data frame.

```{r yx_scatter_numeric}
library(ggplot2)
ggplot(prob2_df, aes(x = x, y = y, color = vec_numeric)) + geom_point() +labs(color = "x + y > 1")
```

This code chunk makes scatterplots of y vs x colored by factor variables created in Problem 2 data frame.

```{r yx_scatter_factor}
ggplot(prob2_df, aes(x = x, y = y, color = vec_factor)) + geom_point() + labs(color = "x + y > 1")
```

**Comments:** We can use all these three three variable types (logical, numeric and factor) to define colors in scatter plots. For logical variables, there are only 2 colors assigned for either False or True; for numeric varibles, the colors are defined by a scale from the lowest value to the highest value; for factor variables, we need to see if the values in it are numeric or logical, and then  the colors are defined by the type of the values.

This code chunk exports the scatterplot colored by the logical variable.
